Excuse me, do you have a moment to talk about version control?

### 2017-05-13 README.Rmd
Newline and 2FA test
Respond to @nicholasjhorton comment 1; closes #4

---
title: "Git and GitHub for statistical practice and teaching"
author: "Jenny Bryan"
date: "`r format(Sys.Date())`"
output: github_document
---

*Alternative title: Excuse me, do you have a moment to talk about Git and GitHub?*

## Why and who?

@@

Benefits of using hosted version control as your *modus operandi*:

  * Doing your work becomes tightly integrated with organizing, recording, and disseminating it.
  * The marginal effort required to create a web presence for a project is negligible.
  * GitHub makes a fantastic course management system for courses that use R.
  * By using common mechanics across work modes, you achieve basic competence quickly and avoid the demoralizing forget-relearn cycle.

## Git

@@

In my opinion, **for new users**, the pros of Git only outweigh the cons when you factor in the overhead of communicating and collaborating with other people, including your future self. And who among us does not need to do that? Your life is much easier if this is baked into your workflow, as opposed to being a separate process that you dread or neglect. Communication and collaboration are the killer apps of version control, which brings me to my next point.

@@

Many people who don't use Git are unwittingly creating a poor man's version of it. They create long chains of copies of an important file, decorating the name with initials, dates and other descriptors. The Git way is to track the evolution of that file, through a series of commits, each equipped with an explanatory message and a nickname. Especially important versions are given a human-readable tag, to signal a meaningful milestone. Yes, there is some pain in adopting the formalism of Git, but it is worth it.

@@

@@

<https://help.github.com/categories/working-with-non-code-files/>
<https://help.github.com/articles/rendering-and-diffing-images/>

@@

>>>>

---
title: "Excuse me, do you have a moment to talk about version control?"
author: "Jenny Bryan"
date: "`r format(Sys.Date())`"
output: github_document
---

## Why Git?

@@

Benefits of using hosted version control in your statistical practice:

  * Doing your work becomes tightly integrated with organizing, recording, and disseminating it. It's not a separate, burdensome task you are tempted to neglect.
  * The marginal effort required to create a web presence for a project is negligible. It's not a separate, burdensome task you are tempted to neglect.
  * GitHub makes a fantastic course management system for courses that use R. You and your students can exchange actual working code and explore the associated results.
  * By using common mechanics across work modes (research, teaching, analysis), you achieve basic competence quickly and avoid the demoralizing forget-relearn cycle.

## What is Git?

@@

In my opinion, **for new users**, the pros of Git only outweigh the cons when you factor in the overhead of communicating and collaborating with other people, including your future self. And who among us does not need to do that? Your life is much easier if this is baked into your workflow, as opposed to being a separate process that you dread and avoid. Communication and collaboration are the killer apps of version control. Git enforces a painfully rigorous model of file management, but it is critical for the distribution of files across different people, computers, and time.

Many people who don't use Git unwittingly re-invent a poor man's version of it. They take an important file and distribute it via email. All parties make changes, decorating the file name with initials, dates, and other descriptors. Before you know it, the original file is the root of a complicated phylogeny that no amount of "Track changes" and good intentions can resolve.

The Git way is to track the evolution of that file, through a series of commits, each equipped with an explanatory message and a nickname. All collaborators sync regularly to a common version, acknowledging that the difficulty of merging goes up faster than the size of the difference (cite good enough). Especially important versions get a human-readable tag, to signal a meaningful milestone. Yes, there is some pain in adopting the formalism of Git, but it is worth it.

## Who should read this and what to expect

@@

@@

Does creation and presence in GitHub repo make the project more readable and navigable? If so DO IT.

@@

<https://help.github.com/categories/working-with-non-code-files/>

<https://help.github.com/articles/rendering-and-diffing-images/>

@@

why sharing intermediate md is better than html (not readable) or pdf (merge conflicts). markdown is the magical intersection of git-friendly (plain text) and human-friendly (becasue GitHub renders it nicely)

possible github explainer
https://www.wired.com/2015/03/github-conquered-google-microsoft-everyone-else/

http://stackoverflow.com/questions/2712421/r-and-version-control-for-the-solo-data-analyst

my tips around md are the large concept of "make things navigable/readable" of GitHub, particularized to R code

https://www.onshape.com/cad-blog/how-google-solved-the-version-control-problem
